---
title: "Linear Regression with Medical Insurance"
author: "Johann Piedras"
date: "11/28/2020"
output:  
  pdf_document:
    #toc: yes
    toc_depth: 4
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '4'
---
\newpage
\tableofcontents
\pagebreak[4]

# Which Factors Influce the Price Of Health Insurance? 
First and foremost, this RMD file is inspired and founded thanks to a Python Notebook by mariapushkareva on Kaggle. The purpose here is to showcase an example of linear regression with medical data, but also to parallel data analysis from Python using R. \

With that out of the way lets, look at the insurance.csv file sourced from Kaggle. Although I don't know exactly where Kaggle got the csv from, the purpose derived from the data is is to attempt to understand what factors contribute to the cost of health insurance. 

### Factors In Health Insurance Cost
**Age** : The age of a beneficiary of health insurance. \
**Sex** : Insurance companies use the binary of female/male \
**BMI** : Short for Body Mass Index. $BMI = \frac{m}{h^2}$ where m is mass in kilograms, and h is height in meters. \
**Children** : Number of dependents for the beneficiaries insurance plan. \
**Smoker** : Whether the beneficiary smokes or not. \
**Region** : The beneficiaries area within the US. \
**Charges** : Amount they've been charged. \


## EDA

```{r}
# importing the data
df <- read.csv('insurance.csv', header = TRUE)
head(df)
```
### Dimension: dim() <-- shape()
```{r}
dim(df)
```
### Summary Statistics: summary() <-- describe()
```{r}
summary(df)
```
### Data Types: str() <-- .types()
```{r}
str(df)
```
Alternatively you can use the sapply function to find the datatypes of each column. 
```{r}
sapply(df,class)
```
#### Apply() family tangent 
**apply()**: apply(Array, margin =(1 or 2), function...) -> For arrays. 1 is rows. 2 is columns. c(1,2) is columns and rows.  \
**lapply()**: lapply(Dataframe/List/Vectors, function...) -> Returns a list of the same size of the object inputted/ \
**sapply()**: sapply(Dataframe/List/Vectors, function...) -> Returns a vector, or a simplified version of the object class. \ 

### Nulls in each column 
```{r}
# Python would use... df.isnull().sum()
colSums(is.na(df))
```

### Basic EDA report
So after some basic review the first things that come to mind are:
- No Null. \
- Sex, Smoker, and Region are factors. We could potentially make dummies from these. \
- There's a significant amount of non smokers compared to smokers. \
- Each region has about 320 people. \
- Charges range from 1k to 63k so there is a lot of variance there. \


```{r include=FALSE}
library(ggplot2)
library(scales)
```

```{r}
# Histogram overlaid with kernel density curve
ggplot(df, aes(x=charges)) + 
    geom_histogram(aes(y=..density..),      # Histogram with density instead of count on y-axis
                   binwidth=2000,
                   colour="black", fill="blue",alpha=.5) +
    geom_density() + # Overlay with transparent density plot 
    scale_y_continuous(name = "Density of Charges", labels = comma) +
    ggtitle("Distribution of Charges") + xlab("Beneficiary Charges") 
```

```{r }
# Histogram overlaid with kernel density curve
ggplot(df, aes(x=charges)) + 
    geom_histogram(aes(y=..density..),      # Histogram with density instead of count on y-axis
                   #binwidth=2000,
                   colour="black", fill="blue",alpha=.5) +
    geom_density() + # Overlay with transparent density plot 
    scale_x_log10()+
    scale_y_continuous(name = "Density of Charges", labels = comma) +
    ggtitle("Distribution of Charges Using Log Transformation") + xlab("Beneficiary Charges") 
```
